---
title: "email"
output: blastula::blastula_email
---

<style type ="text/css">
h1.title {
  font-family: Arvo
}

h1 {
  font-family: Arvo;
  font-size: 42px;
  margin-top: 100px
}

h2 {
  font-family: Arvo
}

h3 {
  font-family: Arvo
}

</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fontfamily = "Sans Source Pro",
  fig.cap = ""
)

library(blastula)
library(purrr)
library(dplyr)
```

```{r}
add_image(
  file = "humdata_logo.png",
  align = "left",
  width = 200
)
```

# Global Monitoring Alerts
## `r format(Sys.Date(), "%d %B %Y")`

The following situations have been flagged by the
Centre for Humanitarian Data global monitoring alert system. Details on the
specific alerts alerts are below.

----

```{r, results = "asis"}

pwalk(
  .l = flags_email %>%
    select(
      iso3,
    country,
    flag_type,
    flag_source,
    message,
    url
    ),
  .f = \(
    iso3,
    country,
    flag_type,
    flag_source,
    message,
    url
  ) {
    knitr::knit_child(
      "alert_section.Rmd",
      envir = environment(),
      quiet = TRUE
    ) |>
      cat()
  }
)
```

Global monitoring is updated daily at 11AM UTC. The source code and documentation
for the analysis is available on [GitHub](https://github.com/OCHA-DAP/pa-global-monitoring/).
Reach out to the Centre for Humanitarian Data's predictive analytics team at
email@un.org if you have any questions or want to discuss the product.


