---
title: "email"
output: blastula::blastula_email
---

<style type ="text/css">
h1 {
  font-family: Arvo, "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-weight: normal
}

h2 {
  font-family: Arvo, "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-weight: normal
}

h3 {
  font-family: Arvo, "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-weight: normal
}

p {
  font-family: "Source Sans Pro", "Helvetica Neue", Helvetica, Arial, sans-serif
}

</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fontfamily = "Sans Source Pro",
  fig.cap = "",
  fig.path = file.path("figure", paste0(flag_source, "_", flag_type), "")
)

library(blastula)
library(purrr)
library(dplyr)
library(sf)
library(stringr)
library(gghdx)
gghdx()

flag_source_str <- str_to_upper(flag_source)
flag_type_str <- str_replace(str_to_title(flag_type), "_", " ")

flags_specific <- filter(
  flags_email,
  flag_type == !!flag_type,
  flag_source == !!flag_source
)
```

```{r}
add_image(
  file = "centre_banner.png",
  alt = "Centre for Humanitarian Data banner",
  align = "center",
  width = "100%"
)
```

# Global Monitoring Alert
## `r flag_type_str` - `r flag_source_str` - `r format(Sys.Date(), "%d %B %Y")`

The following `r tolower(flag_type_str)` situations have been flagged by the
Centre for Humanitarian Data global monitoring alert system, based on data from
the `r flag_source_str`. Details on the specific alerts alerts are below.

```{r, out.width="90%", dpi=300, fig.asp=0.55, fig.align="center", fig.wdith = "100%"}
download.file(
  url = "https://github.com/datasets/geo-countries/raw/master/data/countries.geojson",
  destfile = f <- tempfile(fileext = ".geojson")
)

sf_world <- read_sf(f) %>%
  filter(
    ADMIN != "Antarctica"
  )
 
# create legend fill

legend_fill <- hdx_hex(c("tomato-hdx", "tomato-light"))
names(legend_fill) <- c("New alert", "Ongoing alert")
 
# map all ongoing alerts
# and all ongoing alerts specific to this type and source
# and new alerts
df_flags <- flags_total %>%
  filter(
    email | end_date - Sys.Date() >= -30,
    flag_source == !!flag_source
  ) %>%
  transmute(
    iso3,
    map_fill = case_when(
      email ~ "New alert",
      TRUE ~ "Ongoing alert"
    )
  )

sf_world %>%
  left_join(
    df_flags,
    by = c("ISO_A3" = "iso3")
  ) %>%
  st_as_sf() %>%
  ggplot() +
  geom_sf(
    aes(
      fill = map_fill
    ),
    linewidth = 0.1
  ) +
  coord_sf(
    datum = NULL,
    clip = "off"
  ) +
  theme(
    panel.background = element_rect(
      fill = "aliceblue",
      color = hdx_hex("gray-dark"),
      linewidth = 0.5
    ),
    panel.grid = element_blank(),
    plot.margin = grid::unit(c(0, 0, 0, 0), "mm"),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.title = element_text(face = "bold")
  ) +
  scale_fill_manual(
    values = legend_fill,
    na.value = "white",
    name = "Alerts:"
  ) +
  labs(
    caption = "Alerts defined as ongoing if they have ended in the past 30 days."
  )
```

----

```{r, results = "asis"}

pwalk(
  .l = flags_specific %>%
    select(
      iso3,
      country,
      start_date,
      end_date,
      message,
      url,
      summary_experimental
    ),
  .f = \(
    iso3,
    country,
    start_date,
    end_date,
    message,
    url,
    summary_experimental
  ) {
    knitr::knit_child(
      "alert_section.Rmd",
      envir = environment(),
      quiet = TRUE
    ) |>
      cat()
  }
)
```

## Methodology and contact

Global monitoring is updated every weekday at 11AM UTC. The source code and documentation
for the analysis is available on [GitHub](https://github.com/OCHA-DAP/pa-global-monitoring/).
The relevant methods for `r flag_source_str` data are detailed
[here](`r paste0("https://github.com/OCHA-DAP/pa-global-monitoring/blob/main/src/indicators/", flag_source, "/README.md")`).

Reach out to the Centre for Humanitarian Data's predictive analytics team at
leonardo.milano@un.org if you have any questions or want to discuss the product.

----

```{r}
add_image(
  file = "ocha_logo_wide.png",
  align = "center",
  width = "25%"
)
```

<p>
<center>

<b> OCHA Centre For Humanitarian Data </b>

Fluwelen Burgwal 58 | 2511 CJ The Hague | The Netherlands

</center>
</p>
