---
title: "Reproduce Audience Analysis From Updated Blob"
format: html
editor: visual
---

# Intro

Since we are now pipelining user analytics data to the blob and appending it into single files we have more 
options for time series analysis. However, if we want to reproduce the exact analysis in `adhoc/audience_analysis.R` which just uses a snap shot of latest data retrieved from API we have to do a 
few additional steps. Therefore this notebook preserves that analysis, but using our new data source which
will be updated and changed over time. Basically now we don't have to deal w/ mailchimp in the analysis notebook.


```{r}
#nolint start
box::use(
  cs = src/utils/cloud_storage
)

box::use(
  dplyr,
  gg = ggplot2,
  gghdx,
  httr2,
  lubridate,
  purrr,
  # rnaturalearth, # need to figure out why terra dep is blocking this with renv
  scales,
  sf,
  stringr,
  tidyr,
  stringr
)

filter_to_latest <- function(df){
  df |>
  dplyr$group_by(
    id
  ) |>
  dplyr$filter(extraction_date == max(extraction_date)) |>
  dplyr$ungroup()
}

df_members_info_full <- cs$read_az_file(
  name = "output/user_research/hdx_signals_user_interests.csv"
  )
df_members_interactions_full <- cs$read_az_file(
  name = "output/user_research/hdx_signals_user_interactions.csv"
  )

df_members_info <- filter_to_latest(df_members_full)
df_member_interactions <- filter_to_latest(df_members_interactions_full)

df_members <- df_members_info |> 
  dplyr$mutate(
    extraction_date= lubridate$as_date(extraction_date)
  ) |> 
  dplyr$left_join(
    dplyr$select(df_member_interactions,-extraction_date), by ="id"
  )
```

```{r}
# audience without interest analysis
df_members_distinct <- df_members |>
  dplyr$group_by(
    status, subscription_date, organisation, iso2, open_rate, click_rate, email_count, group
    # status, subscription_date, organisation, iso2, group,open_rate, click_rate, email_count
  ) |>
  dplyr$summarize(
    all_locations = any(interest == "All locations in the region" & interested),
    interest_num = sum(interested[interest != "All locations in the region"]),
    .groups = "drop_last"
  ) |>
  dplyr$summarize(
    num_datasets = interest_num[group == "Datasets of interest"],
    all_datasets = num_datasets == 6,
    num_all_locations = sum(all_locations),
    all_locations = all(all_locations[group != "Datasets of interest"]),
    everything = all_datasets && all_locations,
    .groups = "drop"
  )

###################################
#### ANALYSIS FOR PRESENTATION ####
###################################

gghdx$gghdx()

df_subscribed <- df_members_distinct |>
  dplyr$filter(
    status == "subscribed"
  )

# number of subscribers
nrow(df_subscribed)

# subscribers by organisation
df_subscribed |>
  dplyr$filter(
    status == "subscribed"
  ) |>
  dplyr$mutate(
    organisation = dplyr$case_when(
      stringr$str_detect(organisation, "OCHA") ~ "OCHA",
      organisation == "German Federal Foreign Office" ~ "GFFO",
      organisation %in% c("Centre for Humanitarian Data", "HDX") ~ "CHD/HDX",
      organisation == "USAID" ~ "USAID/BHA",
      organisation == "Impact Initiatives" ~ "IMPACT Initiatives",
      organisation %in% c("International Rescue Committee", "IRC International Rescue Committee") ~ "IRC",
      organisation == "World Health Organization" ~ "WHO",
      organisation %in% c("Iom", "International Organisation for Migration") ~ "IOM",
      organisation %in% c("Complex Risk Analytics Fund (CRAF’d)", "CRAF'd | UN EOSG") ~ "CRAF'd",
      TRUE ~ organisation
    )
  ) |>
  dplyr$count(
    organisation
  ) |>
  dplyr$arrange(
    n
  ) |>
  dplyr$mutate(
    organisation = factor(organisation, levels = organisation)
  ) |>
  dplyr$slice_tail(
    n = 20
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = n,
      y = organisation
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gghdx$geom_text_hdx(
    mapping = gg$aes(
      label = n
    ),
    nudge_x = 1.5,
    fontface = "bold",
    hjust = 0
  ) +
  gg$labs(
    x = "# of subscribers",
    y = "",
    title = "Top 20 subscribing organisations"
  )
```


```{r}
#| eval: false

# map of the data
df_subscribed |>
  dplyr$count(
    iso2
  ) |>
  dplyr$filter(
    iso2 != ""
  ) |>
  dplyr$right_join(
    y = rnaturalearth$countries110,
    by = c("iso2" = "ISO_A2")
  ) |>
  dplyr$filter(
    ISO_A3 != "ATA"
  ) |>
  sf$st_as_sf() |>
  gg$ggplot(
    mapping = gg$aes(
      fill = n,
      label = n
    )
  ) +
  gg$geom_sf() +
  gg$geom_sf_text(
    color = "black"
  ) +
  gg$scale_fill_gradient(
    low = gghdx$hdx_hex("mint-ultra-light"),
    high = gghdx$hdx_hex("mint-dark"),
    na.value = "white"
  ) +
  gg$theme(
    legend.position = "none",
    panel.grid = gg$element_blank(),
    axis.line = gg$element_blank(),
    axis.text = gg$element_blank()
  ) +
  gg$labs(
    x = "",
    y = "",
    title = "Location of subscribers"
  )
```


```{r}
# how many people are subscribing to everything
df_subscribed |>
  dplyr$summarize(
    everything = sum(everything) / dplyr$n(),
    all_locations = sum(all_locations) / dplyr$n(),
    all_datasets = sum(all_datasets) / dplyr$n()
  ) |>
  tidyr$pivot_longer(
    cols = tidyr$everything()
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = value,
      y = name
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gg$scale_y_discrete(
    labels = c("All datasets", "All locations", "Everything")
  ) +
  gg$scale_x_continuous(
    labels = scales$label_percent()
  ) +
  gg$labs(
    x = "",
    y = "",
    title = "Bulk subscriptions"
  )
```


```{r}
# analyze dataset subscriptions
df_members |>
  dplyr$filter(
    group == "Datasets of interest",
    status == "subscribed"
  ) |>
  dplyr$group_by(
    interest
  ) |>
  dplyr$summarize(
    n = sum(interested) / length(unique(id))
  ) |>
  dplyr$arrange(
    n
  ) |>
  dplyr$mutate(
    interest = factor(interest, levels = interest)
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = n,
      y = interest
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gg$scale_x_continuous(
    labels = scales$label_percent()
  ) +
  gg$labs(
    x = "",
    y = "",
    title = "Most popular datasets"
  )
```


```{r}
# number of datasets

df_members |>
  dplyr$filter(
    group == "Datasets of interest"
  ) |>
  dplyr$group_by(
    id
  ) |>
  dplyr$filter(
    !all(interested)
  ) |>
  dplyr$group_by(
    interest
  ) |>
  dplyr$summarize(
    n = sum(interested) / length(unique(id)),
    .groups = "drop"
  )

# locations analysis
df_subscribed |>
  dplyr$count(
    num_all_locations
  ) |>
  dplyr$mutate(
    pct = n / sum(n)
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = pct,
      y = as.factor(num_all_locations)
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gg$labs(
    x = "",
    y = "# of regions subscribed to",
    title = "Subscriptions to entire regions"
  ) +
  gg$scale_x_continuous(
    labels = scales$label_percent()
  )
```


```{r}
# What regions are most popular

df_members |>
  dplyr$filter(
    status == "subscribed",
    interest == "All locations in the region"
  ) |>
  dplyr$group_by(
    group
  ) |>
  dplyr$summarize(
    n = sum(interested) / length(unique(id))
  ) |>
  dplyr$arrange(
    n
  ) |>
  dplyr$mutate(
    group = factor(group, levels = group)
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = n,
      y = group
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gg$scale_x_continuous(
    labels = scales$label_percent()
  ) +
  gg$labs(
    x = "",
    y = "",
    title = "Most popular regions"
  )

```

```{r}
# most popular HRP locations

df_members |>
  dplyr$filter(
    status == "subscribed",
    interest != "All locations in the region",
    group != "Datasets of interest"
  ) |>
  dplyr$group_by(
    interest
  ) |>
  dplyr$summarize(
    n = sum(interested) / length(unique(id))
  ) |>
  dplyr$arrange(
    n
  ) |>
  dplyr$mutate(
    interest = factor(interest, levels = interest)
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = n,
      y = interest
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gg$scale_x_continuous(
    labels = scales$label_percent()
  ) +
  gg$labs(
    x = "",
    y = "",
    title = "Most popular HRP locations"
  )

# general analysis statistics

# df_subscribed$open_rate |> mean()
# df_subscribed$click_rate |> mean()

# subscription timeline
```


```{r}
#| eval: false


df_subscribed |>
  dplyr$mutate(
    subscription_date = lubridate$as_date(subscription_date)
  ) |>
  tidyr$complete(
    subscription_date = seq.Date(from = min(subscription_date), to = max(subscription_date), by = "day"),
  ) |>
  dplyr$group_by(
    subscription_date
  ) |>
  dplyr$summarize(
    subscriptions = sum(!is.na(name)),
    .groups = "drop"
  ) |>
  dplyr$mutate(
    subscriptions_cumsum = cumsum(subscriptions)
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = subscription_date,
      y = subscriptions_cumsum
    )
  ) +
  gg$geom_line(
    linewidth = 1
  ) +
  gghdx$scale_y_continuous_hdx() +
  gg$labs(
    x = "",
    y = "# of subscribers",
    title = "Subscription timeline"
  )
```


```{r}
# number of emails received

df_subscribed |>
  dplyr$count(
    email_count
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      x = n / sum(n),
      y = as.factor(email_count)
    )
  ) +
  gg$geom_bar(
    stat = "identity"
  ) +
  gg$theme(
    panel.grid = gg$element_blank()
  ) +
  gg$scale_x_continuous(
    labels = scales$label_percent()
  ) +
  gg$labs(
    x = "",
    y = "# of emails received",
    title = "# of emails received by subscribers"
  )
```

```{r}
# subscription date and emails received
df_subscribed |>
  gg$ggplot(
    mapping = gg$aes(
      x = lubridate$as_date(subscription_date),
      y = email_count
    )
  ) +
  gg$geom_point() +
  gghdx$scale_y_continuous_hdx() +
  gg$coord_cartesian(
    clip = "off"
  ) +
  gg$labs(
    x = "",
    y = "# of emails received",
    title = "Emails received relative to subscription date"
  )
```


```{r}

# open and click rates relative to emails
df_subscribed |>
  dplyr$mutate(
    groups = cut(
      x = email_count,
      breaks = seq(0, 35, 5),
      labels = paste(
        seq(0, 30, 5) + 1,
        seq(5, 35, 5),
        sep = "-"
      ),
      include.lowest = FALSE
    )
  ) |>
  dplyr$filter(
    !is.na(groups)
  ) |>
  gg$ggplot(
    mapping = gg$aes(
      y = open_rate,
      x = groups,
      group = groups
    )
  ) +
  gg$geom_boxplot(
    fill = "white"
  ) +
  gg$geom_point(
    alpha = 0.2
  ) +
  gg$scale_y_continuous(
    labels = scales$label_percent()
  ) +
  gg$labs(
    x = "# of emails received",
    y = "Open rate",
    title = "Open rate compared to receipt of emails"
  )
```


```{r}
#| eval: false
df_subscribed |>
  dplyr$arrange(
    dplyr$desc(
      open_rate
    )
  ) |>
  dplyr$filter(
    email_count > 10,
    !(organisation %in% c("HDX", "CHD", "Centre for Humanitarian Data")),
    !(name %in% c("Troy", "test test", "Isabelle Tot", "Tristan Downing"))
  ) |>
  dplyr$slice_head(
    n = 20
  ) |>
  dplyr$select(
    name, organisation, open_rate, click_rate, email_count
  )
#nolint end

```

